A general Nullstellensatz for generalized spaces

### 2019-03-15 paper-qcoh.tex
Proof of main theorem in the Horn case

\begin{proof}The proof of Lemma~\ref{lemma:char-fp-models} is constructive and
thus valid in the internal language of~$\Set[\TT]$. Hence we can apply it,
internally, to the theory~$\ul{\TT}/U_\TT$. XXX
\end{proof}

>>>>

\begin{proof}The proof of Lemma~\ref{lemma:char-fp-models} is constructive and
thus valid in the internal language of~$\Set[\TT]$. Hence we can apply it,
internally, to the theory~$\ul{\TT}/U_\TT$ to deduce that a~$U_\TT$-algebra~$A$
is finitely presentable if and only if it is isomorphic to a~$U_\TT$-algebra of
the form~$(\ul{\TT}/U_\TT)\langle X | R \rangle$ with~$X$ Bishop-finite and~$R$
Kuratowski-finite.

We therefore have to verify the following internal
statement: \emph{For any number~$n$, for any sorts~$X_1,\ldots,X_n$
of~$\ul{\TT}/U_\TT$, for any number~$m$, for any atomic
propositions~$R_1,\ldots,R_m$ over the signature of~$\ul{\TT}/U_\TT$ extended
by constants~$e_1 \? X_1, \ldots, e_n \? X_n$, the canonical map~$A \to
(U_\TT)^{\Spec(A)}$ where~$A \defeq (\ul{\TT}/U_\TT)\langle
e_1\?X_1,\ldots,e_n\?X_n \,|\, R_1,\ldots,R_m \rangle$ is an isomorphism.}

Following the Kripke--Joyal translation of this statement, let a stage~$T \in
\Mod{\TT}_\mathrm{fp}$,~$T$-elements~$X_1,\ldots,X_n$ of the object of sorts of
the signature of~$\ul{\TT}/U_\TT$ (that is the constant sheaf on the set of
sorts of~$\TT$), and~$T$-elements~$R_1,\ldots,R_m$ of the object of atomic
propositions over the signature of~$\ul{\TT}/U_\TT$ be given. By passing to a
covering of~$T$, we may assume that the~$X_i$ are given by sorts of~$\TT$ and
that the~$R_j$ are given by atomic propositions over the signature
of~$\TT/U_\TT(T)$.

Since the slice~$\Set[\TT]/\yon T$ is equivalent to~$\Set[\TT/T]$,
hence again the classifying topos of a Horn theory, we may without loss of
generality assume that~$T$ is the initial~$\TT$-model.

In this case the claim follows from Lemma~\ref{lemma:fp-double-dual}, since
the result of constructing, internally to~$\Set[\TT]$, the
model~$(\ul{\TT}/U_\TT)\langle
e_1\?X_1,\ldots,e_n\?X_n \,|\, R_1,\ldots,R_m \rangle$ coincides with
the~$U_\TT$-algebra~$(\TT\langle
e_1\?X_1,\ldots,e_n\?X_n \,|\, R_1,\ldots,R_m \rangle)^\sim$.
\end{proof}
